Graphical formalization and automated computing of safety constraints in robotics

### 2012-09-12 paper/Paper.tex
Added moody's physics of notations as citation

To meet the requirements the visual language should be very easy to use, especially for non-experts. Furthermore it should provide an intuitive application which is ideally learnable within little time. So there are some design decisions an editor for this visual language must fulfill:

\begin{itemize}
	\item Each operator has a different significant visual appearance; in this case we have used color. This kind of classification enables a faster subconscious identification by the user.
	%** COMMENT: can you refer to a GUI design text book regarding this? And how about colour blindness? Don't get me wrong; I am very happy with it; just could do with some citation about it. **
	\item All editing is performed only by simple drag and drop. Operators and propositions can be moved and dropped onto other operators. A tool bar provides all operator and proposition types to be instantiated and there is a trash can for deleting existing operators.
	\item The layout of constraints (nested operators) has two dimensions with a certain meaning. Figure~\ref{fig:directions} demonstrates the ``logical'' vertical read direction as well as the time releveant horizontal line.
	\item In order to simplify the reading of constraints an operator can be hovered over by the mouse pointer. All higher operators become bleached out so that the hovered operator and its children appear highlighted. It's intended to be similar to line coloring when reading a digital text.
	\item Multiple nested operators of the same kind which have no order priorities such as \emph{OR} or \emph{AND} appear unnecessarily complex. These operators can be merged as shown in figure~\ref{fig:nested_and}.
	\item Every edit to either the constraint or the underlying state machine results in an automatically (re-)validation of the constraint. The result is immediately displayed to the user.
	\item There is no button for constraint creation / editing except operator and proposition providers, which let the developer create new instances. Having no additional buttons reduces complexity and keeps it simple.
\end{itemize}

@@

** COMMENT: Possible comment here about the scalability and practicality about constraint generation; do you think it will explode in larger cases? Either way a comment might be useful. **

>>>>

To meet the requirements the visual language should be very easy to use, especially for non-experts. Furthermore it should provide an intuitive application which is ideally learnable within little time. So there are some design decisions an editor for this visual language must fulfill~\cite{moody-physics-of-notations}:

\begin{itemize}
	\item Each operator has a different significant visual appearance; in this case we have used color. This kind of classification enables a faster subconscious identification by the user.
	\item All editing is performed only by simple drag and drop. Operators and propositions can be moved and dropped onto other operators. A tool bar provides all operator and proposition types to be instantiated and there is a trash can for deleting existing operators.
	\item The layout of constraints (nested operators) has two dimensions with a certain meaning. Figure~\ref{fig:directions} demonstrates the ``logical'' vertical read direction as well as the time releveant horizontal line.
	\item In order to simplify the reading of constraints an operator can be hovered over by the mouse pointer. All higher operators become bleached out so that the hovered operator and its children appear highlighted. It's intended to be similar to line coloring when reading a digital text.
	\item Multiple nested operators of the same kind which have no order priorities such as \emph{OR} or \emph{AND} appear unnecessarily complex. These operators can be merged as shown in figure~\ref{fig:nested_and}.
	\item Every edit to either the constraint or the underlying state machine results in an automatically (re-)validation of the constraint. The result is immediately displayed to the user.
	\item There is no button for constraint creation / editing except operator and proposition providers, which let the developer create new instances. Having no additional buttons reduces complexity and keeps it simple.
\end{itemize}

@@

%** COMMENT: Possible comment here about the scalability and practicality about constraint generation; do you think it will explode in larger cases? Either way a comment might be useful. **
